### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
do all low and real deterministic
voi with sethi parameters

``` {r }
det <- scenario(0.00101, 0.001, 0.001)
````

``` {r }
g   <- scenario(lvl, 0.001, 0.001)
````

``` {r }
m   <- scenario(0.001, lvl, 0.001)
````

``` {r }
i   <- scenario(0.001, 0.001, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0.001)
````

``` {r }
gi  <- scenario(lvl, 0.001, lvl)
````

``` {r }
mi  <- scenario(0.001, lvl, lvl)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list(s0.001=c(0.001,0.001,0.001), sg=c(lvl, 0.001, 0.001), sm=c(0.001, lvl, 0.001), si=c(0.001,0.001,lvl), sgm=c(lvl, lvl, 0.001), sgi=c(lvl, 0.001, lvl), smi = c(0.001, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

``` {r }
det <- scenario(0.0, 0.00, 0.00)
````

``` {r }
all_low <- scenario(0.1, 0.1, 0.1)
````

``` {r }
g   <- scenario(lvl, 0, 0)
````

``` {r }
m   <- scenario(0, lvl, 0)
````

``` {r }
i   <- scenario(0, 0, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0)
````

``` {r }
gi  <- scenario(lvl, 0, lvl)
````

``` {r }
mi  <- scenario(0, lvl, lvl)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- names(noise) 
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````
